### 2014-07-07 tex/main-body-text.tex
couple quick edits while gel is running

\section*{Conclusions}
The use of genetic markers to identify population structure, specifically
the number of genetic clusters in a collection $K$ has drastically exanded
in the past decade to aid in the fields of evolution, epidemiology, and conservation
genetics. By virtute of this exanding desire to identify $K$ there has been a push to 
develop methods that can accurately infer $K$ while at the same time be easy to run
both in terms of proccess time and user interface. Naturally, a program claiming
``more accurate allocations and more reliable estimates of $K$ [while running]
much faster than {\sc structure} \citep[][p.~734]{Duc&Tur2012}'' is particularly 
appealing. Despite these two claims, we have shown that the algorithm implemented 
in {\sc flock} is equivalent to 
a restrictured case of the simulated annealing algorthim to find the Bayesian 
MAP estimate from the marginalized form of the no admixture and non-correlated
allele frequency model in {\sc structure} with no processing speed advantage for real datasets.

@@

One of the major claimed advantages of {\sc flock} over methods for solving the 
K-partition problem is that, ``The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. This appears to result from two issues:
(1) the number of individuals in each collection and (2) the lenght of runs for each program in each comparision. 
In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the true 
value of $K$. 
It seemed reasonable to compare, for each $K$, one iteration of {\sc structure} 
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both evaluate the partition space once. We chose to run six iterations for each program
in order to compare the consistency of results between programs and among runs.
In addition to changing the number of groups of runs of {\sc flock} to compare,
the dataset used was an order of magnatude
larger than the largest used by \citep{Duc&Tur2012} (N = 60, 120, and 240). It may hold that {\sc flock}
is able to process small datasets faster than {\sc structure}, but with the rapid increase in our ability to economically
genotype a large number of individuals for a great many number of loci, this advantage may not be relevant to many 
study designs.

>>>>

\section*{Conclusions}
The use of genetic markers to identify population structure, specifically
the number of genetic clusters in a collection ($K$) has drastically expanded
in the past decade to aid in the fields of evolution, epidemiology, and conservation
genetics. By virtute of this expanding desire to identify $K$ there has been a push to 
develop methods that can accurately infer $K$ while at the same time remain acessable
to a wide range of end users and run quickly. Naturally, a program claiming
``more accurate allocations and more reliable estimates of $K$ [while running]
much faster than {\sc structure} \citep[][p.~734]{Duc&Tur2012}'' is particularly 
appealing. Despite these two claims, we have shown that the algorithm implemented 
in {\sc flock} is equivalent to 
a restricted case of the simulated annealing algorthim to find the Bayesian 
MAP estimate from the marginalized form of the no admixture and non-correlated
allele frequency model in {\sc structure} with no processing speed advantage for real datasets.

@@

One of the major claimed advantages of {\sc flock} over methods for solving the 
K-partition problem is that, ``The very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each $K$'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. This appears to result from two issues:
(1) the number of individuals in each collection and (2) the length of runs for each program in each comparision. 
In the comparison by \citep{Duc&Tur2012}, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each $K$ from 1 to four more than 
the true value of $K$. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by a 200,000 sweep sample from the posterior of $K$ from 1 to three more than the true 
value of $K$. 
It seemed reasonable to compare, for each $K$, one iteration of {\sc structure} 
to one iteration of {\sc flock} (50 different starting allocations that are reallocated 20 times) 
as both evaluate the partition space once. We chose to run six iterations for each program
in order to compare the consistency of results between programs and among runs.
In addition to changing the number of groups of runs of {\sc flock} to compare,
the dataset used was an order of magnatude
larger than the largest used by \citep{Duc&Tur2012} (N = 60, 120, and 240). It may hold that {\sc flock}
is able to process small datasets faster than {\sc structure}, but with the rapid increase in our ability to economically
genotype a large number of individuals for a great many number of loci, this advantage may not be relevant to many 
study designs.
